\textbf{Too Beautiful to be Fake: Attractive Faces are Less Likely to be Judged as Artificially Generated}

### 2022-09-27 submission/manuscript.Rmd
update results

Only one image file yielded a strong simulation monitoring bias (> 85\%), being classified as fake in 87.4\% of trials. This image was removed from further analysis, leaving 108 trials per participant. On average, across participants, 44\% of images (95\% CI [0.11, 0.64]) were judged as fake and 56\% of images (95\% CI [0.36, 0.89]) as real. An intercept-only model with the participants and images as random factors showed that the Intraclass Correlation Coefficient (ICC), which can be interpreted as the proportion of variance explained by the random factors, was of 10.5% for the participants and 8.7% for the stimuli.

There was a significant negative effect of the delay of re-exposure (with 95\% of values between 1.58 and 30.31 min), suggesting that shorter delays were associated with a slight bias towards the belief of reality (60\% at a theoretical delay of 0), which decreased to 50\% at a theoretical delay of 60 min ($OR = 0.99$, $95\% CI = [0.99, 1.00]$, $z = -2.27$, $p = .023$). There was also a significant negative effect on judgment confidence, but only in the real condition ($\beta = -0.005$, $95\% CI = [-0.1, 0.0]$, $p = .023$).

@@

Attractiveness had a significant positive and linear relationship ($R^2_{marginal}$ = 2.8%) with the belief that a stimulus was real ($\beta_{poly1} = 16.37$, $95\% CI = [7.76, 24.98]$, $z = 3.73$, $p < .001$) for males, and a quadratic relationship for females ($\beta_{poly2} = 7.77$, $95\% CI = [1.41, 14.13]$, $z = 2.40$, $p = .017$), with both non-attractive and attractive faces being judged as more real. No significant relationship was found between attractiveness ratings and belief confidence, aside of a similar trend for females only, for faces judged as real ($\beta_{poly2} = 4.38$, $95\% CI = [0.96, 7.79]$, $z = 2.51$, $p = .012$). There was no interaction with reported self-attractiveness.

Beauty, adjusted for trustworthiness and familiarity, had a significant positive and linear relationship ($R^2_{marginal}$ = 3.5%) with the belief that a stimulus was real ($\beta_{poly1} = 9.54$, $95\% CI = [1.43, 17.65]$, $z = 2.31$, $p = .021$) for males only. No effect on confidence was found, aside from a quadratic relationship for females for faces judged as fake, suggesting that non-beautiful and highly beautiful faces were rated as fake with more confidence than average faces ($\beta_{poly2} = 6.61$, $95\% CI = [1.98, 11.24]$, $z = 2.80$, $p = .005$). There was no interaction with reported self-attractiveness.

Trustworthiness, adjusted for beauty and familiarity, had a significant positive and linear relationship ($R^2_{marginal}$ = 3.0%) with the belief that a stimulus was real ($\beta_{poly1} = 11.60$, $95\% CI = [4.15, 19.06]$, $z = 3.05$, $p = .002$) for females only. No effect on confidence was found, aside from a quadratic relationship for females for faces judged as real, suggesting that non-trustworthy and highly trustworthy faces were rated as real with more confidence than average faces ($\beta_{poly2} = 6.47$, $95\% CI = [1.73, 11.21]$, $z = 2.68$, $p = .007$).

We did not find any significant relationships for familiarity adjusted for beauty and trustworthiness ($R^2_{marginal}$ = 3.0%). However, a significant positive and linear relationship was found with the confidence in faces judged as real ($\beta_{poly1} = 9.31$, $95\% CI = [3.45, 15.17]$, $z = -3.11$, $p = .002$), and a quadratic relationship for faces judged as fake ($\beta_{poly1} = -12.67$, $95\% CI = [-19.87, -5.47]$, $z = -3.45$, $p < .001$; $\beta_{poly2} = 8.14$, $95\% CI = [0.01, 16.28]$, $z = 1.96$, $p = .05$), for males only, suggesting that faces are judged as real with more confidence when they are familiar, and judged as fake with less confidence when they are not familiar or highly familiar.

@@

The models including the personality traits suggested that *Honesty-Humility* had a significant negative relationship predominantly with the confidence associated with faces judged as real ($\beta_{real} = -1.69$, $95\% CI = [-2.74, -0.63]$, $z = -3.14$, $p < .01$; $\beta_{fake} = -1.02$, $95\% CI = [-2.07, 0.03]$, $z = -1.90$, $p = 0.058$). Narcissism shared significant links through various dimensions, such as positive relationship between the confidence for both real and fake judgments and *Acclaim Seeking* ($\beta_{real} = 2.08$, $95\% CI = [0.79, 3.37]$, $z = 3.16$, $p < .01$; $\beta_{fake} = 1.60$, $95\% CI = [0.30, 2.90]$, $z = 2.42$, $p < .05$), and a negative relationship with *Authoritativeness* ($\beta_{real} = -1.38$, $95\% CI = [-2.50, -0.27]$, $z = -2.43$, $p < .05$; $\beta_{fake} = -1.23$, $95\% CI = [-2.35, -0.11]$, $z = -2.15$, $p < .05$) and *Thrill Seeking* ($\beta_{real} = -0.93$, $95\% CI = [-1.75, -0.10]$, $z = -2.20$, $p < .05$; $\beta_{fake} = -1.03$, $95\% CI = [-1.87, -0.20]$, $z = -2.44$, $p < .05$). Finally, the social phobia dimension was significantly associated with a decreased probability of judging faces as fake ($\beta = -0.97$, $95\% CI = [-1.86, -0.08]$, $z = -2.14$, $p < .05$), but no effect on the confidence judgments was found. No significant relationships were found for intolerance to uncertainty or paranoid beliefs.

@@

Questions pertaining to the attitude towards AI were reduced to 3 dimensions through factor analysis, labelled AI-Enthusiasm (loaded by items expressing interest and excitement in AI development and applications), AI-Realness (loaded by items expressing positive opinions on the ability of AI to create realistic material), and AI-Danger (loaded by items expressing concerns on the unethical misuse of AI technology). Only AI-Enthusiasm displayed a significant positive relationship with the confidence in both real and fake judgments ($\beta_{real} = 0.29$, $95\% CI = [0.08, 0.50]$, $z = 2.74$, $p < .01$; $\beta_{fake} = 0.38$, $95\% CI = [0.18, 0.59]$, $z = 3.60$, $p < 0.001$).

@@

>>>>

Only one image file yielded a strong simulation monitoring bias (> 85\%), being classified as fake in 87.4\% of trials. This image was removed from further analysis, leaving 108 trials per participant. On average, across participants, 44\% of images (95\% CI [0.12, 0.64]) were judged as fake and 56\% of images (95\% CI [0.36, 0.84]) as real. An intercept-only model with the participants and images as random factors showed that the Intraclass Correlation Coefficient (ICC), which can be interpreted as the proportion of variance explained by the random factors, was of 9.0% for the participants and 9.6% for the stimuli.

While the delay of re-exposure of the stimulus did not have a significant effect on participants' beliefs of reality ($OR = 1.00$, $95\CI = [0.99, 1.00]$ ), judgement confidence was found to be negatively associated with re-exposure delay, but only when the faces were judged as real ($\beta = -0.006$, $95\% CI = [-0.1, 0.002]$, $p = .004$)

<!-- There was a significant negative effect of the delay of re-exposure (with 95\% of values between 1.58 and 30.31 min), suggesting that shorter delays were associated with a slight bias towards the belief of reality (60\% at a theoretical delay of 0), which decreased to 50\% at a theoretical delay of 60 min ($OR = 0.99$, $95\% CI = [0.99, 1.00]$, $z = -2.27$, $p = .023$). There was also a significant negative effect on judgment confidence, but only in the real condition ($\beta = -0.005$, $95\% CI = [-0.1, 0.0]$, $p = .023$). -->

@@

Attractiveness had a significant positive and linear relationship ($R^2_{marginal}$ = 2.0%) with the belief that a stimulus was real ($\beta_{poly1} = 16.57$, $95\% CI = [7.33, 25.82]$, $z = 3.51$, $p < .001$) for males, and a quadratic relationship for females ($\beta_{poly2} = 7.82$, $95\% CI = [1.81, 13.84]$, $z = 2.55$, $p = .011$), with both non-attractive and attractive faces being judged as more real. Attractiveness was also found to have a significant positive and quadratic relationship with confidence in judging faces both as real ($\beta_{poly2} = 4.30, $, $95\% CI = [0.97, 7.64]$, $z = 2.53$, $p = .011$) and as fake ($\beta_{poly2} = 5.23, $, $95\% CI = [0.86, 9.60]$, $z = 2.35$, $p = .019$) for females. For males, however, a significant negative and quadratic relationship was found between attractiveness ratings and belief confidence only for faces judged as fake ($\beta_{poly2} = -9.92, $, $95\% CI = [-18.99, -0.86]$, $z = -2.15$, $p = .032$). There was no interaction with reported self-attractiveness.

Beauty, adjusted for trustworthiness and familiarity, had a significant positive and linear relationship ($R^2_{marginal}$ = 2.0%) with the belief that a stimulus was real ($\beta_{poly1} = 11.82$, $95\% CI = [4.28, 20.21]$, $z = 2.76$, $p = .006$) for males only. No effect on confidence was found, aside from a quadratic relationship for females for faces judged as fake, suggesting that non-beautiful and highly beautiful faces were rated as fake with more confidence than average faces ($\beta_{poly2} = 7.84$, $95\% CI = [3.39, 12.29]$, $z = 3.46$, $p < .001$). There was no interaction with reported self-attractiveness.

Trustworthiness, adjusted for beauty and familiarity, had a predominantly significant positive and linear relationship ($R^2_{marginal}$ = 2.0%) with the belief that a stimulus was real ($\beta_{poly1} = 6.44$, $95\% CI = [-0.11, 13.00]$, $z = 1.93$, $p = .0054$) for $p\approx .05$ for females only. No effect on confidence was found for males, whereas a quadratic relationship was found for females for both faces judged as real ($\beta_{poly2} = 6.14$, $95\% CI = [2.13, 10.14]$, $z = 3.00$, $p = .003$) as well as fake ($\beta_{poly2} =6.12$, $95\% CI = [1.49, 10.75]$, $z = 2.59$, $p = .001$), suggesting that non-trustworthy and highly trustworthy faces were rated with more confidence as real or fake than average faces.

We did not find any significant relationships for familiarity adjusted for beauty and trustworthiness ($R^2_{marginal}$ = 2.0%). However, a significant positive and linear relationship was found with the confidence in faces judged as real ($\beta_{poly1} = 9.98$, $95\% CI = [3.83, 16.13]$, $z = 3.18$, $p = .001$) and a negative linear relationship was found with those judged as fake ($\beta_{poly1} = -12.41$, $95\% CI = [-20.27, -4.54]$, $z = -3.09$, $p = .002$) for males only, suggesting that faces are judged as real with more confidence when they are familiar, and judged as fake with more confidence when they are unfamiliar.

@@

The models including the personality traits suggested that *Honesty-Humility* had a significant negative relationship with the confidence associated with real as well as fake judgements ($\beta_{real} = -1.62$, $95\% CI = [-2.55, -0.70]$, $z = -3.43$, $p < .001$; $\beta_{fake} = -1.16$, $95\% CI = [-2.09, -0.23]$, $z = -2.45$, $p = 0.014$). For trait narcissism, significant positive associations were found between the probability of judging faces as real and dimensions of narcissism such as *Acclaim Seeking* ($\beta = 2.24$, $95\% CI = [1.17, 4.27]$, $z = 2.44$, $p = .015$), and *Manipulativeness* ($\beta = 0.47$, $95\% CI = [0.25, 0.87]$, $z = -2.4$, $p = 0.017$). Confidence judgements also shared links with narcissism through various facets, such as a positive relationship between the confidence for both real and fake judgments with *Acclaim Seeking* ($\beta_{real} = 1.65$, $95\% CI = [0.59, 2.70]$, $z = 3.07$, $p =.002$; $\beta_{fake} = 1.62$, $95\% CI = [0.56, 2.68]$, $z = 3.00$, $p = .003$), and a negative relationship with *Authoritativeness* ($\beta_{real} = -1.57$, $95\% CI = [-2.58, -0.57]$, $z = -3.08$, $p = .002$; $\beta_{fake} = -1.49$, $95\% CI = [-2.50, -0.48]$, $z = -2.89$, $p = .004$).

Overall social anxiety levels (obtained from aggregating the 2 anxiety scales - *SIAS-6* and *SPS-6*), on the other hand, was significantly associated with the confidence in real judgements only ($\beta_{real} = -0.22$, $95\% CI = [-0.30, -0.14]$, $z = -5.29$, $p < .001$). Similarly, *Intolerance to Uncertainty* was also negatively associated with confidence judgements of faces being real ($\beta_{real} = -0.30$, $95\% CI = [-0.45, -0.15]$, $z = -3.88$, $p < .001$). In particular, confidence in real judgements was found to share predominantly significant positive links with the *Prospective Anxiety* dimension ($\beta_{real} = 1.43$, $95\% CI = [0.10, 2.76]$, $z = 2.10$, $p = .036$), although there was a negative association found with the *Inhibitory Anxiety* dimension ($\beta_{real} = -1.00$, $95\% CI = [-2.01, 0.02]$, $z = -1.93$, $p = 0.054$). There was also a largely significant positive relationship between the *Persecutory Ideation* dimension of *Paranoid Beliefs* with the probability of faces being judged as real ($\beta = 1.87$, $95\% CI = [0.99, 3.54]$, $z = 1.93$, $p = .054$) for $p\approx .05$. However, the negative relationship between confidence judgements and *Paranoid Beliefs* was only found for faces judged as real ($\beta_{real} = -0.21$, $95\% CI = [-0.29, -0.14]$, $z = -5.63$, $p < .001$).

<!-- and *Thrill Seeking* ($\beta_{real} = -0.93$, $95\% CI = [-1.75, -0.10]$, $z = -2.20$, $p < .05$; $\beta_{fake} = -1.03$, $95\% CI = [-1.87, -0.20]$, $z = -2.44$, $p < .05$).     -->

<!--Finally, the social phobia dimension was significantly associated with a decreased probability of judging faces as fake ($\beta = -0.97$, $95\% CI = [-1.86, -0.08]$, $z = -2.14$, $p < .05$), but no effect on the confidence judgments was found. No significant relationships were found for intolerance to uncertainty or paranoid beliefs. -->

@@

Questions pertaining to the attitude towards AI were reduced to 3 dimensions through factor analysis, labelled AI-Enthusiasm (loaded by items expressing interest and excitement in AI development and applications), AI-Realness (loaded by items expressing positive opinions on the ability of AI to create realistic material), and AI-Danger (loaded by items expressing concerns on the unethical misuse of AI technology). Whereas overall attitudes towards AI was found to be significantly and negatively associated with judgement confidence for real faces only ($\beta_{real} = -0.16$, $95\% CI = [-0.2, -0.13]$, $z = 8.90$, $p < .001$), suggesting that individuals with highly positive attitudes are less confident in rating faces as real, AI-Enthusiasm displayed a significant positive relationship with the confidence in both real and fake judgments ($\beta_{real} = 0.21$, $95\% CI = [0.02, 0.40]$, $z = 2.20$, $p = .028$; $\beta_{fake} = 0.31$, $95\% CI = [0.12, 0.50]$, $z = -8.90$, $p < 0.001$).

@@

<!--TO-DO: Uncertainty Intolerance and Paranoid Thinking -->
